---
title: 'HW 06: APIs and Web Scraping'
author: "Ryo Tanaka"
date: "`r Sys.Date()`"
output:
  html_document: default
  word_document: default
urlcolor: blue
params:
  solutions: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo       = params$solutions, 
                      eval       = params$solutions,
                      fig.align  = "center",
                      fig.height = 3, 
                      fig.width  = 5)
```

© 2023 David Gerard, not to be posted online.

# Instructions

- Write your solutions in this starter file. You should modify the 
  "author" field in the YAML header.
- Only commit R Markdown and HTML files (no PDF files). Make sure
  you have knitted to HTML for your final submission.
- **Make sure to commit each time you answer a question.**
- Only include the necessary code, not any extraneous code, to answer the 
  questions.
- Learning objectives:
    - Obtain data from an API.
    - Scrape data from the web.

# Open Brewery Database

Consider the Open Brewery Database API: <https://www.openbrewerydb.org/>

Only use `{httr2}`, not `{httr}`.

Loading libraries
```{r}
library(tidyverse)
library(httr2)
library(repurrrsive)
library(maps)
library(rvest)
#install.packages("maps")
```


1. (1 pt) Get the list of all micro breweries in Ohio (163 of them) where we have longitude and latitude information (124 of them). These should be the microbreweries you obtained:

```{r}
# base url
baseurl_brewery <- "https://api.openbrewerydb.org/v1/breweries"
```

```{r}
request(base_url = baseurl_brewery) %>% 
  req_url_query(by_state = "Ohio",
                by_type = "micro",
                per_page = 200) %>% 
  req_perform() -> brewery_state_out


brewery_df <- tibble(brew = resp_body_json(brewery_state_out))
brewery_df <- unnest_wider(brewery_df, brew)
brewery_df_1 <- brewery_df %>% 
  filter(!is.na(latitude) | !is.na(longitude))
brewery_df_1$name
```


2. (1 pt) Clean up the data from part 1 to get the following data frame:


```{r}
names(brewery_df_1)
brewery_df_1 <- brewery_df_1[-c(3,5,6,10,15)]
brewery_df_1
```

3. (1 pt) Edit the following ggplot code to obtain the following plot:

```{r}
brewery_df_1 <- brewery_df_1 %>% 
  mutate(longitude = as.numeric(longitude),
         latitude = as.numeric(latitude))
countymap <- map_data("county")
countymap %>% 
  filter(region == "ohio") %>% 
  ggplot() + 
  geom_polygon(aes(x = long, 
                   y = lat, 
                   group = subregion),
               fill = "white",
               color = "black") +
  geom_point(data = brewery_df_1,
             aes(x = longitude,
                 y = latitude)) +
  theme_void()
```

# English women artists

Consider the copied Wikipedia page on English women artists: 
<https://data-science-master.github.io/lectures/data/engart.html>

We'll use the copied version on GitHub rather than the original version
to make sure solutions are consistent. But the original version can be found
here (but don't use it): <https://en.wikipedia.org/wiki/List_of_English_women_artists>

Use rvest to answer the following questions.

1. (1 pt) Download the html file and save the output to a variable.

```{r}
# downloading the html page
eng_women_html <- read_html("https://data-science-master.github.io/lectures/data/engart.html")
```


2. (1 pt) Use SelectorGadget to extract each woman, years of life, and artistic medium. For example, my selections looked like this:

```{r}
eng_women_df <- html_elements(x = eng_women_html,
              css = "ul:nth-child(49) li , ul:nth-child(47) li, ul:nth-child(45) li, ul:nth-child(43) li, ul:nth-child(41) li, ul:nth-child(39) li, ul:nth-child(37) li, ul:nth-child(35) li, ul:nth-child(33) li, ul:nth-child(31) li, ul:nth-child(29) li, ul:nth-child(27) li, ul:nth-child(25) li, ul:nth-child(23) li, ul:nth-child(21) li, ul:nth-child(19) li, ul:nth-child(17) li, ul:nth-child(15) li, ul:nth-child(13) li, ul:nth-child(11) li, ul:nth-child(9) li, ul:nth-child(7) li, ul:nth-child(5) li") %>% 
  html_text()
```

3. (2 pts) Clean the data. 

    Hints:

    1. Not all year ranges are of the form (Birth-Death). You should place
       NA's in the appropriate locations. No need to extract third-party 
       datasets to obtain the true values.
    2. Be careful of parsing numbers like `"c.1888"`.
    3. Parentheses are used more than just to delimit years.
    4. Painters, sculptors, illustrators, and printmakers are the most common
       types of artists, so I included indicators for those mediums. Note
       that not all printmakers are called "printmakers".

    Your final data frame should look like this:
    
    
```{r}
eng_women_df <- tibble(data = eng_women_df)
eng_original_df <- eng_women_df

eng_women_df <- 
  eng_women_df %>% 
  separate(
    col = "data", 
    into = c("name", "other"),
    sep = "\\(", 
    extra = "merge")

eng_women_df <- 
  eng_women_df %>% 
  separate(
    col = "other", 
    into = c("year", "mediums"),
    sep = "\\),", 
    extra = "merge")

eng_women_df <- eng_women_df %>% 
  mutate(year = str_remove_all(year, "[^0-9]")) %>% 
  separate(col = year, 
           into = c("birth", "death"), 
           sep = 4)

eng_women_df$death[eng_women_df$death == ''] <- NA

eng_women_df$mediums <- str_replace_all(eng_women_df$mediums, 
                                        ",", 
                                        " ")
eng_women_df$mediums <- str_replace_all(eng_women_df$mediums, 
                                        "  ", 
                                        " ")
eng_women_df$name <- str_replace_all(eng_women_df$name, 
                                        "\n",
                                        "")

eng_women_df <- eng_women_df %>% 
  mutate(painter = str_detect(eng_women_df$mediums, 
                              "painter|paint"),
         sculptor = str_detect(eng_women_df$mediums, 
                              "sculptor"),
         illustrator = str_detect(eng_women_df$mediums, 
                              "illustrator"),
         printmaker = str_detect(eng_women_df$mediums, 
                              " printmaker|prıntmaker|printer"))

error_women <- !eng_women_df$painter & str_detect(eng_original_df$data, 
                                                     pattern = "paint")
eng_women_df$name[error_women]
eng_women_df$name[is.na(error_women)]
eng_women_df$painter[eng_women_df$name == "Maria Pixell "] <- TRUE
eng_women_df$painter[eng_women_df$name == "Hilary Simon, silk painter"] <- TRUE
```

4. (1 pt) Tabulate the number of painters, sculptors, illustrators, and printmakers. You should get these numbers:

```{r}
tibble("painters_n" = sum(eng_women_df$painter,na.rm = TRUE),
       "sculptor_n" = sum(eng_women_df$sculptor,na.rm = TRUE),
       "illustrator_n" = sum(eng_women_df$illustrator, na.rm = TRUE),
       "printmaker_n" = sum(eng_women_df$printmaker, na.rm = TRUE))
```

5. (1 pt) Plot the lifespans of printmakers. Your plot should look like this:

```{r}
eng_women_viz <- eng_women_df %>% 
  select(name,birth,death,painter,printmaker) %>% 
  filter(printmaker == TRUE) %>% 
  mutate(birth = as.numeric(birth),
         death = as.numeric(death))

eng_women_viz <- eng_women_viz[order(eng_women_viz$birth), 
                               decreasing = TRUE]
eng_women_viz[14,3] <- Inf
eng_women_viz[15,3] <- Inf

  ggplot(data = eng_women_viz,
         aes(y = name)) +
    labs(x = "Birth/Death",
         y = "Artist") +
    theme_bw() +
    geom_segment(aes(x = birth,
                     y = reorder(name,
                                 birth,
                                 decreasing = TRUE),
                     xend = death,
                     yend = name,
                     color = painter)) +
    scale_colour_manual(values = c("navy","orange"))
```
